\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-04-01 paper.tex
adjusted figure widths
added distributions for videos by location and region

Over the last decade, emphasis has been made on the need for autonomous vehicles to reduce road collisions and reckless driving. However, research into collision prediction has been slowed by the lack of egocentric collision-oriented datasets. Currently, this type of data is often created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions and data collection equipment. We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories. We specifically focus on collecting collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region. Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world, subject to varying visibilities, varying weather conditions, and varying settings.

@@

\begin{figure}[htpb]
	\centering
    \tikzset{
    	node distance = 6mm and 0cm,
        module/.style={%
            draw, rounded corners,
            minimum width=#1,
            minimum height=7mm,
            font=\sffamily
            },
        module/.default=1cm,
        >=LaTeX
    }
    \begin{tikzpicture}[
      % This will show the frame around the figure
      show background rectangle]

@@

\begin{figure}[htpb]
		\centering
    \includegraphics[width=0.5\textwidth]{example_gui_tool.png}
		\caption{GUI tool to facilitate annotation}
		\label{fig:example_gui_tool-png}
\end{figure}

@@

\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.4\textwidth]{prcurve.png}
		\caption{Pre-trained DSARNN Precision-Recall curve on prototype dataset}
		\label{fig:pr_curve}
\end{figure}

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Objects by class},
      ylabel={Frequency (\# of objects)},
      ymin=-50,
      ymax=1800,
      xtick=data,
      xticklabels from table={\byclass}{X},
      xticklabel style={rotate=50,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by object class}
		\label{fig:obj-by-class}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      ymin=-5,
      ymax=175,
      xtick=data,
      xticklabels from table={\byactors}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by number of participants}
		\label{fig:vids-by-participant}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by agents},
      xlabel={Number of agents},
      ylabel={Frequency (\# of videos)},
      ymin=-10,
      ymax=270,
      xtick=data,
      xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by number of agents}
		\label{fig:vids-by-agents}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by duration},
      xlabel={Duration (in frames)},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      ymin=-5,
      ymax=130,
      xticklabels from table={\byduration}{X},
      xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by duration}
		\label{fig:vids-by-duration}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in,trim={0 1cm 0 0.5cm},clip]{by-collision.png}
		\caption{All videos in database grouped by collision type}
		\label{fig:vids-by-collision}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in,trim={0 1cm 0 1cm},clip]{by-camera.png}
		\caption{All videos in database grouped by camera type}
		\label{fig:vids-by-camera}
\end{figure}

\todo{Organize figures better, crop out excess whitespace, resize them and place them within the column of the page.}
\todo{Explain the "other" category in the class histogram. These are stationary/non-vehicular objects.}
\todo{Explain the distinctions between the different types of collisions in the collision chart.}
\todo{Add chart showing videos by source (Figure 11).}
\todo{Move Figures 5-11 to Methodology - Video Collection.}
\todo{Reduce caption size for each figure.}
\todo{Add a paragraph explaining the key characteristics of Figures 5-11.}

>>>>

Over the last decade, emphasis has been made on the need for autonomous vehicles to reduce road collisions and reckless driving. However, research into collision prediction has been slowed by the lack of egocentric collision-oriented datasets. Currently, this type of data is often created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions and data collection equipment. We provide a pipeline to assemble datasets of real vehicle collision events that have been published online to various video repositories. We specifically focus on collecting footage of collisions recorded from front-mounted dashcam video cameras and demonstrate the importance of learning from complex road scenes and conditions globally rather than in one region. Further, we present a small prototype dataset that we have produced using our pipeline which includes egocentric dashcam vehicle footage from all over the world, subject to varying visibilities, varying weather conditions, and varying settings.

@@

\begin{figure}[htbp]
	\centering
    \tikzset{
    	node distance = 6mm and 0cm,
        module/.style={%
            draw, rounded corners,
            minimum width=#1,
            minimum height=7mm,
            font=\sffamily
            },
        module/.default=1cm,
        >=LaTeX
    }
    \begin{tikzpicture}[
      % This will show the frame around the figure
      show background rectangle]

@@

\begin{figure}[htbp]
		\centering
    \includegraphics[width=0.46\textwidth]{example_gui_tool.png}
		\caption{GUI tool to facilitate annotation}
		\label{fig:example_gui_tool-png}
\end{figure}

@@

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.5\textwidth]{prcurve.png}
		\caption{Pre-trained DSARNN Precision-Recall curve on prototype dataset}
		\label{fig:pr_curve}
\end{figure}

@@

\begin{figure}[htbp]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Objects by class},
      ylabel={Frequency (\# of objects)},
      ymin=-50,
      ymax=1800,
      xtick=data,
      xticklabels from table={\byclass}{X},
      xticklabel style={rotate=50,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
		\caption{Distribution of videos in dataset by object class}
		\label{fig:obj-by-class}
\end{figure}

\begin{figure}[htbp]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      ymin=-5,
      ymax=175,
      xtick=data,
      xticklabels from table={\byactors}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Distribution of videos in dataset by number of participants}
		\label{fig:vids-by-participant}
\end{figure}

\begin{figure}[htbp]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by agents},
      xlabel={Number of agents},
      ylabel={Frequency (\# of videos)},
      ymin=-10,
      ymax=270,
      xtick=data,
      xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
		\caption{Distribution of videos in dataset by number of agents}
		\label{fig:vids-by-agents}
\end{figure}

\begin{figure}[htbp]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by duration},
      xlabel={Duration (in frames)},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      ymin=-5,
      ymax=130,
      xticklabels from table={\byduration}{X},
      xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
		\caption{Distribution of videos in dataset by duration}
		\label{fig:vids-by-duration}
\end{figure}

\begin{figure}[htbp]
		\centering
    \includegraphics[width=0.46\textwidth,trim={0 1cm 0 0.5cm},clip]{by-collision.png}
		\caption{Distribution of videos in database by collision type}
		\label{fig:vids-by-collision}
\end{figure}

\begin{figure}[htbp]
		\centering
    \includegraphics[width=0.46\textwidth,trim={0 1cm 0 1cm},clip]{by-camera.png}
		\caption{Distribution of videos in database by camera type}
		\label{fig:vids-by-camera}
\end{figure}

\begin{table}[htbp]
	\caption{Distribution of videos in database by download source}
	\label{vids-by-source}
	\begin{center}
		\begin{tabular}{|c|c|}
			\hline
			Download source & Percentage of videos \\
			\hline
			youtube.com & 98.40\% \\
			\hline
			imgur.com & 0.85\% \\
			\hline
			gfycat.com & 0.47\% \\
			\hline
			streamable.com & 0.28\% \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

\begin{table}[htbp]
	\caption{Distribution of videos in dataset by geographical region}
	\label{vids-by-region}
	\begin{center}
		\begin{tabular}{|c|c|}
			\hline
			Region & Percentage of videos \\
			\hline
			North America & 48.13\% \\
			\hline
			Europe & 24.30\% \\
			\hline
			Russia & 19.16\% \\
			\hline
			Asia & 4.67\% \\
			\hline
			Australia & 3.74\% \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

\todo{Organize figures better, crop out excess whitespace, resize them and place them within the column of the page.}
\todo{Explain the "other" category in the class histogram. These are stationary/non-vehicular objects.}
\todo{Explain the distinctions between the different types of collisions in the collision chart.}
\todo{Add Figure 11 (table) showing videos by source (98.4\% YouTube, 0.47\% gfycat.com, 0.85\% imgur.com, 0.28\% streamable.com)}
\todo{Move Figures 5-11 to Methodology - Video Collection.}
\todo{Reduce caption size for each figure.}
\todo{Add a paragraph explaining the key characteristics of Figures 5-11.}
